COG-ED Manuscript

### 2022-03-24 06_Paper/COG-ED/Manuscript.Rmd
added ethics

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.

@@

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.

@@

JZ, CS, and AS conceptualized the study and acquired funding.
JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.

>>>>

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
      - Visualization
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.

@@

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number SR-EK-50012022).
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.

@@

JZ, CS, and AS conceptualized the study and acquired funding.
JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
JZ prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.
